DeepPicar: A Low-cost Deep Neural Network-based Autonomous Car

### 2018-04-17 paper/evaluation.tex
revision 4.E (2nd)

Figure~\ref{fig:perf-vs-modelcnt} shows the results. In the figure, the
X-axis shows the system configuration: \#of DNN models x \#of CPU
cores/DNN. For example, '4Nx1C' means running four DNN models each of
which is assigned to run on one CPU core, whereas '2Nx2C' means running
two DNN models, each of which is assigned to run on two CPU
cores. The Y-axis shows the average inference timing.
The two bars on the left show the impact of co-scheduling four DNN
models. Compared to executing a single DNN model on one CPU core
(1Nx1C), when four DNN models are co-scheduled (4Nx1C), each model
suffers an average inference time increase of approximately 11 ms,
$\sim$24\%. On the other hand, when two DNN models, each using two CPU
cores, are co-scheduled (2Nx2C), the average inference timing is increased by
about 4 ms, or 13\%, compared to the baseline of running one model
using two CPU cores (1Nx2C).

These increases in inference times in the co-scheduled scenarios are
expected due to contention in the shared hardware
resources, such as the shared cache and DRAM.

@@

\subsection{Effect of Co-scheduling Synthetic Benchmarks}\label{sec:eval-memhog}

In this experiment, we further investigate the impact of shared
resource contention to the DNN inference timing of DeepPicar using  
synthetic memory benchmarks. Specifically, we use the \emph{Bandwidth}
benchmark from the IsolBench suite~\cite{Valsan2016}, which
sequentially reads or writes a big array; we henceforth refer BwRead 
as Bandwidth with read accesses and BwWrite as the one with write
accesses. The experiment setup is as follows. We run a single DNN
model on one core, and co-schedule an increasing number of the
Bandwidth benchmark instances on the other cores. We repeat the
experiement first with BwRead~\footnote{\texttt{\$ bandwdith -a read
    -m 16384 -t 1000}} and next with BwWrite~\footnote{\texttt{\$
    bandwdith -a write -m 16384 -t 1000}}.

@@

Figure~\ref{fig:perf_vs_bandwidth} shows the execution times of the DNN 
model against varying number of BwRead and BwWrite co-runners. First,
note that BwWrite cause significantly high execution time incrase---up
to 11.6X---on the DNN inferencing timing while BwRead causes
relatively much smaller time increase. While execution time increase
was expected, the degree of which is quite surprising---\emph{if the DNN
controller was driving an actual car, it would result in crash of the
car!}

\fixme{story: is cache space contention the reason? traditional
  solution is cache partitioning. so, next we evaluate if cache
  partitioning can solve the problem. spolier alert: it does not.}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=.45\textwidth]{figs/a53_vs_a7}
  \caption{DNN model performance on different in-order
ARM Cortex cores. \fixme{this may be better in the plaform comparison section}.}
  \label{fig:a53_vs_a7}
\end{figure}

>>>>

Figure~\ref{fig:perf-vs-modelcnt} shows the results. In the figure, the
X-axis shows the system configuration: \#of DNN models x \#of CPU
cores/DNN. For example, '4Nx1C' means running four DNN models each of
which is assigned to run on one CPU core, whereas `2Nx2C' means running
two DNN models, each of which is assigned to run on two CPU
cores. The Y-axis shows the average inference timing.
The two bars on the left show the impact of co-scheduling four DNN
models. Compared to executing a single DNN model on one CPU core
(1Nx1C), when four DNN models are co-scheduled (4Nx1C), each model
suffers an average inference time increase of approximately 11 ms,
$\sim$24\%. On the other hand, when two DNN models, each using two CPU
cores, are co-scheduled (2Nx2C), the average inference timing is increased by
about 4 ms, or 13\%, compared to the baseline of running one model
using two CPU cores (1Nx2C).

These increases in inference times in the co-scheduled scenarios are
expected because it is well-known that co-scheduled tasks on a
multicore platform interfere with each other due to contention in the
shared hardware resources, such as the shared
cache~\cite{Gracioli2015} and DRAM~\cite{Yun2013}.

@@

\subsection{Effect of Co-scheduling Synthetic Memory Intensive Tasks}\label{sec:eval-memhog}

In this experiment, we investigate \emph{worst-case} impact of shared 
resource contention to DeepPicar's DNN inference timing using  
a synthetic memory benchmark. Specifically, we use the \emph{Bandwidth}
benchmark from the IsolBench suite~\cite{Valsan2016}, which
sequentially reads or writes a big array; we henceforth refer BwRead 
as Bandwidth with read accesses and BwWrite as the one with write
accesses. The experiment setup is as follows. We run a single DNN
model on one core, and co-schedule an increasing number of the
Bandwidth benchmark instances on the other cores. We repeat the
experiement first with BwRead and next with BwWrite.

%% ~\footnote{\texttt{\$ bandwdith -a read  -m 16384 -t 1000}} 
%% ~\footnote{\texttt{\$ bandwdith -a write -m 16384 -t 1000}}.

@@

Figure~\ref{fig:perf_vs_bandwidth} shows the execution times of the DNN 
model against varying number of BwRead and BwWrite co-runners. Note
that BwWrite cause significantly high execution time incrase---up 
to 11.6X---on the DNN inferencing timing while BwRead causes
relatively much smaller time increase. While execution time increase
was expected, the degree of which is quite surprising---\emph{if the DNN
controller was driving an actual car, it would result in a crash of the
car!}

Given the importance of predictable timing on real-time control, such
as our DNN based control task, we wanted to understand (1) the main
source of the timing and (2) to evaluate existing isolation methods to
avoid this kind of timing interference. Specifically, shared cache
space and DRAM bandwidth are two most well-known sources of contention
in multicore. Thus, in the following, we investigate test if and how
they influence the observed timing interference and how effective are
the existing mitigation methods. To our surprise, we find that neither
the cache space nor DRAM bandwidth is the root cause of the
DeepPicar's observed worst-case execution time increase.

%% \fixme{story: is cache space contention the reason? traditional
%%   solution is cache partitioning. so, next we evaluate if cache
%%   partitioning can solve the problem. spolier alert: it does not.}

@@
